---
title: "First Look"
author: "Elliot Pickens"
date: "October 10, 2018"
output: pdf_document
---

#### Note: This guide has been an amazing help https://topepo.github.io/caret/recursive-feature-elimination.html#recursive-feature-elimination-via-caret

#### Load some libraries

* You may need to install some of the libraries below. To install package `tidyverse`, for example, run `install.packages("tidyverse")` in the console

```{r, echo=FALSE, message=FALSE, error=FALSE}
library(aod)
library(boot)
library(broom)
library(car)
library(caret)
library(caretEnsemble)
library(dplyr)
library(forecast) 
library(GGally)
library(ggformula)
library(ggplot2)
library(ggthemes)
library(glmnet)
library(gridExtra)
library(lattice)
library(leaps)
library(MASS)
library(RANN)
library(readr)
library(readxl)
library(skimr)
library(stringr)
library(tabulizer)
library(tibble)
library(tidyr)
library(tidyselect)
library(tidyverse)
library(tseries)
```

####Load some data

```{r, message=FALSE, warning=FALSE}
registration <- read_xlsx("data/minnesota-voter-registration-by-county-since-2000.xlsx", skip = 1)
elections <- read_xlsx("data/minnesota-election-statistics-1950-to-2016.xlsx", skip = 2, col_names = c("Year", "Est_Num_Elg_Voters", "Num_Voters", "Prcnt_Turnout", "Num_Elc_Day_Regis", "Prcnt_Voters_Regis_Elc_Day"))
#dists <- read_csv("data/Minnesota_District_edit.csv")
dists <- read_csv("data/dists_t.csv", skip = 1)
#Load demographic data
demo15 <- read_csv("data/ACS_5YR/ACS_15_5YR_S0501/ACS_15_5YR_S0501_with_ann.csv", skip = 0)
demo17 <- read_xls("data/ACS_1YR/ACS_17_1YR_S0601(1).xls", skip = 0)

```

####Load elections stats

```{r, echo=FALSE, warning=FALSE}
elec18 <- read_xls("data/dist_elec_stats/2018_primary.xls")
elec16 <- read_xlsx("data/dist_elec_stats/2016-general-federal-state-results-by-precinct-official-1.xlsx")
elec14 <- read_xlsx("data/dist_elec_stats/2014-general-federal-state-results-by-precinct-official.xlsx")
elec12 <- read_xlsx("data/dist_elec_stats/2012mngeneralelectionresults_official_postrecounts.xlsx")
elec10 <- read_xls("data/dist_elec_stats/2010_general_results_final.xls")
elec08 <- read_xls("data/dist_elec_stats/2008_general_results.xls")
```

####Group Counts by Congressional District

```{r}
vote18 <- elec18 %>%
  group_by(CONGDIST)

vote16 <- elec16 %>%
  group_by(CONGDIST) %>%
  summarise(tot_votes = sum(TOTVOTING), repub = sum(USREPR), dem = sum(USREPDFL))

vote16 <- vote16 %>%
  dplyr::select(tot_votes, repub, dem) %>%
  filter(tot_votes < 1000000)

vote14 <- elec14 %>%
  group_by(CONGDIST) %>%
  summarise(tot_votes = sum(TOTVOTING), repub = sum(USREPR), dem = sum(USREPDFL)) %>%
  dplyr::select(tot_votes, repub, dem)

vote12 <- elec12 %>%
  group_by(CONGDIST) %>%
  summarise(tot_votes = sum(TOTVOTING), repub = sum(USREPR), dem = sum(USREPDFL))

vote12 <- vote12 %>%
  dplyr::select(tot_votes, repub, dem) %>%
  filter(tot_votes < 1000000)

vote10 <- elec10 %>%
  group_by(CG) %>%
  summarise(tot_votes = sum(TotVoters), repub = sum(CONGR), dem = sum(CONGDFL))

vote10 <- vote10 %>%
  dplyr::select(tot_votes, repub, dem) %>%
  filter(tot_votes < 1000000)

vote08 <- elec08 %>%
  group_by(CG) %>%
  summarise(tot_votes = sum(TotVoters), repub = sum(CONGR), dem = sum(CONGDFL))

vote08 <- vote08 %>%
  dplyr::select(tot_votes, repub, dem) %>%
  filter(tot_votes < 1000000)
```

####Load the Demographic Data that Matches the Years We Have Turnout Data for

```{r}
demo16 <- read_xls("data/ACS_1YR/ACS_16_1YR_BasicER.xls")
demo14 <- read_xls("data/ACS_5YR/Basic/ACS_14_5YR_Ber.xls")
demo12 <- read_xls("data/ACS_5YR/Basic/ACS_12_5YR_Ber.xls")
demo10 <- read_xls("data/ACS_5YR/Basic/ACS_10_5YR_Ber.xls")
demo08 <- read_xls("data/ACS_1YR/ACS_08_1YR_BasicER.xls")
```

####Let's Combine the Turnout Data With Our Features

```{r}
temp16 <- demo16 %>%
  mutate(tot_votes = vote16$tot_votes, r_votes = vote16$repub, d_votes = vote16$dem, Elec_Type_Gen = 1, Elec_Type_Mid = 0)

temp14 <- demo14 %>%
  mutate(tot_votes = vote14$tot_votes, r_votes = vote14$repub, d_votes = vote14$dem, Elec_Type_Gen = 0, Elec_Type_Mid = 1)

temp12 <- demo12 %>%
  mutate(tot_votes = vote12$tot_votes, r_votes = vote12$repub, d_votes = vote12$dem, Elec_Type_Gen = 1, Elec_Type_Mid = 0)

temp10 <- demo10 %>%
  mutate(tot_votes = vote10$tot_votes, r_votes = vote10$repub, d_votes = vote10$dem, Elec_Type_Gen = 0, Elec_Type_Mid = 1)

temp08 <- demo08 %>%
  mutate(tot_votes = vote08$tot_votes, r_votes = vote08$repub, d_votes = vote08$dem, Elec_Type_Gen = 1, Elec_Type_Mid = 0)
```

####Let's Combine all of the Temp Tables and get a basic turnout %

```{r}
temp <- bind_rows(temp16, temp14, temp12, temp10, temp08)

temp <- temp %>% rename(Tot_Pop = `Total population`) 
  
temp$Tot_Pop <- as.numeric(gsub(",","",temp$Tot_Pop))

vars <- names(temp)[3:38]
temp <- temp %>% mutate_each(funs(as.numeric(gsub("%", "", ., fixed = TRUE))/100), vars)

temp <- temp %>%
  mutate(over18 = EighteenTo24 + TwentyfiveTo44 + FortyFiveTo54 + FiftyfiveTo64 + SixtyfiveTo74 + Seventyfive_plus)

temp1 <- temp %>% 
  mutate(ruff_turnout = tot_votes / (Tot_Pop * over18), repub = r_votes / tot_votes, dem = d_votes / tot_votes) 

#Not sure if I should try to convert percentages
#May or may not come back to this later
```

####Let's Finally create a usuable data set

```{r}
gen_elec_08_16 <- temp1 %>%
  dplyr::select(-Tot_Pop, -tot_votes, -r_votes, -d_votes)

sum(is.na(gen_elec_08_16))

#remove the sole na 

#I am choosing to replace the sole missing value that is already close to 0
#with the 2014 value from the same district
#assuming the the percentage of native people has not changed greatly
#the new value is 0.003 (basically NN -- nearest neighbor method)

gen_elec_08_16 <- gen_elec_08_16 %>%
  replace_na(list(American_Indian_and_Alaska_Native = 0.003))



#remove names

gen_elec_no_names <- gen_elec_08_16 %>%
  dplyr::select(-Subject)

#preProcess <- preProcess(gen_elec_no_names, method='knnImpute')
#preProcess
#gen_elec_no_names <- predict(preProcess, newdata = gen_elec_no_names)

#One Hot Encoding

#dummy_model <- dummyVars(ruff_turnout ~ ., data = gen_elec_no_names)
#trainTemp <- predict(dummy_model, newdata = gen_elec_no_names)
#gen_elec_no_names <- data.frame(trainTemp)
```

####Let's create a seperate data set that can be used for testing (where we don't have turnout)

```{r}
demo17_b <- read_xls("data/ACS_1YR/ACS_17_1YR_BasicER.xls")

demo17_b <- demo17_b %>% rename(Tot_Pop = `Total population`) 
  
demo17_b$Tot_Pop <- as.numeric(gsub(",","",demo17_b$Tot_Pop))

vars <- names(demo17_b)[3:38]
demo17_b <- demo17_b %>% mutate_each(funs(as.numeric(gsub("%", "", ., fixed = TRUE))/100), vars)

demo17_b <- demo17_b %>%
  mutate(over18 = EighteenTo24 + TwentyfiveTo44 + FortyFiveTo54 + FiftyfiveTo64 + SixtyfiveTo74 + Seventyfive_plus)

demo17_b <- demo17_b %>%
  mutate(tot_votes = vote18$Total, r_votes = vote18$Rep, d_votes = vote18$Dem) %>%
  mutate(ruff_turnout = tot_votes / (Tot_Pop * over18), repub = r_votes / tot_votes, dem = d_votes / tot_votes, Elec_Type_Gen = 1, Elec_Type_Mid = 0)



test17 <- demo17_b %>%
  dplyr::select(-Tot_Pop, -tot_votes, -r_votes, -d_votes)

test17 <- test17 %>%
  filter(Subject != "Congressional District 2 (115th Congress), Minnesota")

#remove names

primary_2018_turnout <- test17 %>%
  dplyr::select(ruff_turnout)

test17 <- test17 %>%
  dplyr::select(-Subject, -ruff_turnout)

#fill in NA values

####Will go back and re-Preprocess everything correctly in a minute

####For now I'm going to be lazy
####ANNNDDDDD.....

test17[2, 14] = 0.004
test17[5, 14] = 0.012

#test17 <- test17 %>%
#  replace_na(list(American_Indian_and_Alaska_Native = 0.000))

#no_NA_anymore <- preProcess(test17, method='knnImpute')
#no_NA_anymore

#test17 <- predict(no_NA_anymore, newdata = test17)
#anyNA(test17)
```

####Let's take a look at the data

```{r}
skimmed <- skim_to_wide(gen_elec_no_names)
View(skimmed)

#pairs(gen_elec_no_names[1:15], lower.panel = NULL)
```

####Let's finally do some modelling

####Let's start off with a basic model

####Regression Time

####Also be careful with runtimes here (you may want to only run one of these lines at a time --Bless Crtl Enter--)

```{r}
set.seed(100)

lm.basic <- lm(ruff_turnout ~ 1, data = gen_elec_no_names)

lm.full <- lm(ruff_turnout ~ Male + Female + Under5 + EighteenTo24 + TwentyfiveTo44 + FortyFiveTo54 + FiftyfiveTo64 + SixtyfiveTo74 + Seventyfive_plus + Median_age + White + Black + American_Indian_and_Alaska_Native + Asian + Some_other_race + Two_or_more_races + Hispanic + White_alone + Never_married + Now_married_not_separated + Divorced_separated + Widowed + Less_than_high_school_graduate + High_school_graduate + Some_college_or_associate_degree + Bachelor_degree + Graduate_or_professional_degree + One_9999_loss + TenK_14999 + FifteenK_24999 + TwentyfiveK_34999 + ThirtyfiveK_49999 + FiftyK_74999 + SeventyfiveK_plus + Below_poverty_level + repub + dem + Elec_Type_Gen + Elec_Type_Mid, data = gen_elec_no_names)

stepfwd <- stepAIC(lm.basic, scope = list(lower = ~ 1, upper = ~ Male + Female + Under5 + EighteenTo24 + TwentyfiveTo44 + FortyFiveTo54 + FiftyfiveTo64 + SixtyfiveTo74 + Seventyfive_plus + Median_age + White + Black + American_Indian_and_Alaska_Native + Asian + Some_other_race + Two_or_more_races + Hispanic + White_alone + Never_married + Now_married_not_separated + Divorced_separated + Widowed + Less_than_high_school_graduate + High_school_graduate + Some_college_or_associate_degree + Bachelor_degree + Graduate_or_professional_degree + One_9999_loss + TenK_14999 + FifteenK_24999 + TwentyfiveK_34999 + ThirtyfiveK_49999 + FiftyK_74999 + SeventyfiveK_plus + Below_poverty_level + repub + dem + Elec_Type_Gen + Elec_Type_Mid), direction = "both")

stepbk <- stepAIC(lm.full, scope = list(lower = ~ 1, upper = ~ Male + Female + Under5 + EighteenTo24 + TwentyfiveTo44 + FortyFiveTo54 + FiftyfiveTo64 + SixtyfiveTo74 + Seventyfive_plus + Median_age + White + Black + American_Indian_and_Alaska_Native + Asian + Some_other_race + Two_or_more_races + Hispanic + White_alone + Never_married + Now_married_not_separated + Divorced_separated + Widowed + Less_than_high_school_graduate + High_school_graduate + Some_college_or_associate_degree + Bachelor_degree + Graduate_or_professional_degree + One_9999_loss + TenK_14999 + FifteenK_24999 + TwentyfiveK_34999 + ThirtyfiveK_49999 + FiftyK_74999 + SeventyfiveK_plus + Below_poverty_level + repub + dem + Elec_Type_Gen + Elec_Type_Mid), direction = "both")

summary(stepfwd)
summary(stepbk)

#residualPlots(stepfwd)
#residualPlots(stepbk)
```

####Let's do something more interesting now ***Bless Caret***

####Split training data w 80 - 20 split

```{r}
set.seed(100)

trainRowNums <- createDataPartition(gen_elec_no_names$over18, p = 0.8, list = FALSE)

trainingData <- gen_elec_no_names[trainRowNums,]

testingData <- gen_elec_no_names[-trainRowNums,]

#Store extra data for later use
x = trainingData[, 1:37]
y = trainingData$ruff_turnout
```

####Alright this is where I'm leaving things for now

####We're ready to tune this model all tomorrow

####We don't have any classes so we're really only looking at numeric prediction and possibly some clustering as far as I can see

####These are the models that blessed CARET allows us to choose from

```{r}
modelnames <- paste(names(getModelInfo()), collapse=',  ')
modelnames
```


####RFE Recursive featuer selection

```{r}
set.seed(100)

options(warn=-1)

subsets <- c(3:5, 10, 15, 20, 25, 30, 35, 37)

ctrl <- rfeControl(functions = rfFuncs,
                   method = "repeatedcv",
                   repeats = 5,
                   verbose = FALSE)

lmProfile <- rfe(x=trainingData[, 1:37], y=trainingData$ruff_turnout,
                 sizes = subsets,
                 rfeControl = ctrl)

lmProfile
```

####Fuck it let's run MARS

```{r}
# Set the seed for reproducibility
set.seed(100)

# Train the model using randomForest and predict on the training data itself
model_mars = train(ruff_turnout ~ ., data=trainingData, method='earth')
fitted <- predict(model_mars)

#accuracy plot
plot(model_mars, main="MARS Accuracies")



#Check the importance of the variables
varimp_mars <- varImp(model_mars)
plot(varimp_mars, main="Variable Importance with MARS")

summary(model_mars)
model_mars




head(testingData$ruff_turnout)
pred <- predict(model_mars, testingData)
head(pred)

###This somehow works

pridicted <- factor(predict(model_mars, testingData))
real <- factor(testingData$ruff_turnout)

data1 <- data.frame(data = pridicted, type = "prediction")
data2 <- data.frame(data = real, type = "real")
data3 <- rbind(data1,data2)

# Check if the levels are identical
identical(levels(data3[data3$type == "prediction",1]) , levels(data3[data3$type == "real",1]))

confusionMatrix(data3[data3$type == "prediction",1], data3[data3$type == "real",1],  dnn = c("Prediction", "Reference"))

###^^^ somehow

#But it doesn't really tell us much so I'm not going to use it  
```

####Okay so that is not working properly so I'm going to move on and come back to it

####Let's get some hyperparams (parameters set before training to let this process go soomthly) going 

```{r}
paramControl <- trainControl(method = 'cv', number = 5, savePredictions = 'final', classProbs = T, summaryFunction = twoClassSummary)

# ^^^ 5 fold cross validation that saves predictions and returns class probabilities 

marsGrid <-  expand.grid(nprune = c(2, 4, 6, 8, 10), 
                        degree = c(1, 2, 3))

set.seed(100)
model_mars2 = train(ruff_turnout ~ ., data=trainingData, method='earth', tuneLength = 5, tuneGrid = marsGrid, tuneLength = 5, metric='ROC', trControl = paramControl)
model_mars2

# Step 2: Predict on testData and Compute the confusion matrix
predicted2 <- predict(model_mars2, testingData)
confusionMatrix(reference = testingData$ruff_turnout, data = predicted2, mode='everything', positive='MM')


```

####Never mind mars is still being a pain, moving on

####Let's just run a bunch of shit and then compare

####First up is random forest

```{r}
set.seed(100)

# Train the model using random forest
model_rf = train(ruff_turnout ~ ., data=trainingData, method='rf')

model_rf
plot(model_rf)
summary(model_rf)



```

####Now xgBoost Dart

####This takes dumb long to run be careful

```{r}
set.seed(100)

# Train the model using MARS
model_xgbDART = train(ruff_turnout ~ ., data=trainingData, method='xgbDART', tuneLength=5, verbose=F)
model_xgbDART
```

####Throw in a Support Vector Machine (SVM)

```{r}
set.seed(100)

# Train the model using MARS
model_svmRadial = train(ruff_turnout ~ ., data=trainingData, method='svmRadial', tuneLength=15)
model_svmRadial

```

####Let's compare and see how they fair

```{r}
# Compare model performances using resample()
#TEMPORARY LEFT OUT FOR TESTING DUE TO RUNTIME ISSUES
# XGBDART=model_xgbDART, 
models_compare <- resamples(list(RF=model_rf, MARS=model_mars, SVM=model_svmRadial))

# Summary of the models performances
summary(models_compare)

# Draw box plots to compare models
scales <- list(x=list(relation="free"), y=list(relation="free"))
bwplot(models_compare, scales=scales)
```

####Why not run them all at once --- Ensemble Time ---

```{r}
#ensembleControl <- trainControl(method="repeatedcv", 
#                             number=10, 
#                             repeats=3,
#                             savePredictions=TRUE, 
#                             classProbs=TRUE)

algos <- c('rf', 'earth', 'svmRadial')

set.seed(100)
ensemble <- caretEnsemble::caretList(ruff_turnout ~ ., data=trainingData, methodList=algos) 
results <- resamples(ensemble)
summary(results)

scales <- list(x=list(relation="free"), y=list(relation="free"))
bwplot(results, scales=scales)


```

####TIME TO STACK THEM ALL TOGETHER

```{r}
set.seed(100)

#stackControl <- trainControl(method="repeatedcv", 
#                             number=10, 
#                             repeats=3,
#                             savePredictions=TRUE, 
#                             classProbs=TRUE)

stack <- caretEnsemble::caretStack(ensemble, methods = "glm")

print(stack)

stack_pred <- predict(stack, testingData)
head(stack_pred)

#MSE
mean((testingData$ruff_turnout - stack_pred) ^ 2)

resid <- (testingData$ruff_turnout - stack_pred)
resid <- data.frame(resid, seq(1:7))
resid %>%
  gf_point(resid ~ seq.1.7.) %>%
  gf_hline(yintercept = 0)


#confusionMatrix(stack_pred, testingData$ruff_turnout)

#table(stack_pred, testingData$ruff_turnout)

#confusionMatrix(testingData$ruff_turnout, stack_pred)

test17_pred <- predict(stack, test17)

plot(stack)
```

####Nueral Networks

```{r}
set.seed(100)

# Nueral Net: Quantile Regression Neural Network
model_QRNN = train(ruff_turnout ~ ., data=trainingData, method='qrnn')
model_QRNN
plot(model_QRNN)
```





####Basic Data Vis
####Basic Data Vis
####Basic Data Vis
####Basic Data Vis
####Basic Data Vis

```{r}
gen_turnout <- read_xlsx("data/turnout_2000-2016.xlsx")

gen_turnout %>%
  gf_point(Percent.Turnout ~ Year, ylab = "Percent Turnout", title = "Statewide General Election Turnout") %>%
  gf_lm()
```

####By District

```{r}

graph_data <- read_xlsx("data/test_data.xlsx")

cg1 <- graph_data %>%
  filter(Subject == "CG1")
cg2 <- graph_data %>%
  filter(Subject == "CG2")
cg3 <- graph_data %>%
  filter(Subject == "CG3")
cg4 <- graph_data %>%
  filter(Subject == "CG4")
cg5 <- graph_data %>%
  filter(Subject == "CG5")
cg6 <- graph_data %>%
  filter(Subject == "CG6")
cg7 <- graph_data %>%
  filter(Subject == "CG7")
cg8 <- graph_data %>%
  filter(Subject == "CG8")

#par()

#Using rough turnout

par(mfrow=c(2,2))

cg1 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG1", ylab = "Estimate of Turnout Percentage")
cg2 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG2", ylab = "Estimate of Turnout Percentage")
cg3 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG3", ylab = "Estimate of Turnout Percentage")
cg4 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG4", ylab = "Estimate of Turnout Percentage")
cg5 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG5", ylab = "Estimate of Turnout Percentage")
cg6 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG6", ylab = "Estimate of Turnout Percentage")
cg7 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG7", ylab = "Estimate of Turnout Percentage")
cg8 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG8", ylab = "Estimate of Turnout Percentage")


```








































####Visualization of Regsubsets

```{r}
bestFit = (regsubsets(ruff_turnout~., data = trainingData))
bestFitSummary = summary(bestFit)
data_frame(Cp = bestFitSummary$cp,
           BIC = bestFitSummary$bic,
           AdjR2 = bestFitSummary$adjr2) %>%
    mutate(id = row_number()) %>%
    gather(value_type, value, -id) %>%
    ggplot(aes(id, value, col = value_type)) +
    geom_line() + geom_point() + ylab('') + xlab('Number of Variables Used') +
    facet_wrap(~ value_type, scales = 'free') + 
    scale_x_continuous(breaks = 1:10)
```

$$C_p = \frac{1}{n}(RSS + 2d\sigma^2)$$
$$BIC = \frac{1}{n}(RSS + log(n)d\sigma^2)$$

###ELLIOT LOOK AT THIS

```{r}
rgAttempt = lm(ruff_turnout~Under5 + FortyFiveTo54 + TenK_14999, data = trainingData)
summary(rgAttempt)
predict.lm(rgAttempt, testingData)
test17_reg_pred = predict.lm(rgAttempt, test17)
mean((testingData$ruff_turnout - predict.lm(rgAttempt, testingData)) ^ 2)
```

```{r}
newFit = lm(ruff_turnout~Under5 + FiveTo17 + FortyFiveTo54 + One_9999_loss, data = trainingData)
mean((testingData$ruff_turnout - predict.lm(newFit, testingData)) ^ 2)
plot(newFit$residuals)
```

$$\text{Voter Turnout} = -1.19 + 10.60\text{% Population under age of 5} + 6.27\text{% Population ages 45-54} + 5.13*\text{(% Income Level:10,000 - 14,999)}$$
```{r}
cor_training = dplyr::select(trainingData, which(!sapply(trainingData, is.factor))) %>%
  cor(., use = "pair")

cor_training_df = as.data.frame(cor_training, row.names=NULL) %>%
  mutate(var1 = row.names(cor_training)) %>%
  gather(Male:over18, key=var2, value = correlation)

ggplot(cor_training_df) +
  geom_tile(aes(x=var1, y=var2, fill=correlation)) +
theme(axis.text.x=element_text(angle=90,
vjust=0, hjust=1))
```

###Creating 2014 Representative Vote By District

```{r}
titles = c("republican", "democrat", "other") 
first = c(103536, 122851, 308)
second = c(137778, 95565, 12319)
third = c(167515, 101846, 224)
fourth = c(79492, 147857, 14059)
fifth = c(56577, 167079, 12354)
sixth = c(133328, 90926, 12592)
seventh = c(109955, 130546, 334)
eighth = c(125358, 129090, 11450) #other is green party vote, for 8th district
rep_2014 = rbind.data.frame(first, second, third, fourth, fifth, sixth, seventh, eighth)
colnames(rep_2014) = titles
rep_2014 = mutate(rep_2014, total = republican + democrat + other) %>%
   mutate(repubRatio = republican/total, year = 2014)
```

###Creating 2012 Representative Vote By District

```{r}
first2012 = c(142164, 193211, 505)
second2012 = c(193587, 164338, 521)
third2012 = c(222335, 159937, 433)
fourth2012 = c(109659, 216685, 21682)
fifth2012 = c(88753, 262102, 1114)
sixth2012 = c(179240, 174944, 969)
seventh2012 = c(114151, 197791, 15638)
eighth2012 = c(160520, 191976, 1167)
rep_2012 = rbind.data.frame(first2012, second2012, third2012, fourth2012, fifth2012, sixth2012, seventh2012, eighth2012)
colnames(rep_2012) = titles
rep_2012 = mutate(rep_2012, total = republican + democrat + other) %>%
  mutate(repubRatio = republican/total, year = 2012)
```

###Creating 2010 Representative Vote By District

```{r}
first2010 = c(109242, 122365, 16398)
second2010 = c(181341, 104809, 303)
third2010 = c(161177, 100240, 12675)
fourth2010 = c(80141, 136746,  14539)
fifth2010 = c(55222, 154833, 18691)
sixth2010 = c(159476, 120846, 23369)
seventh2010 = c(90652, 133096, 17349)
eighth2010 = c(133490, 129091, 14500)
rep_2010 = rbind.data.frame(first2010, second2010, third2010, fourth2010, fifth2010, sixth2010, seventh2010, eighth2010)
colnames(rep_2010) = titles
rep_2010 = mutate(rep_2010, total = republican + democrat + other) %>%
   mutate(repubRatio = republican/total, year = 2010)
```

##2016 County Data
```{r}
county_2016 = extract_tables("data/electionresults_2016.pdf", pages = 1)
county_2016 = as.data.frame(county_2016[[2]], stringsAsFactors = FALSE)
colnames(county_2016) = c("County", "VotersRegAM", "RegElecDay", "Sigs", "RegMilOver", "FedAbsentee", "Voters")
```

###Creating a District Column
```{r}
county_2016 = slice(county_2016, 1:87) %>%
  mutate(District = case_when(
    County == "Blue Earth"|County == "Brown"|County == "Dodge"|County == "Faribault"|County == "Fillmore"|County == "Freeborn"|County == "Houston"|County == "Jackson"|County == "Le Sueur"|County == "Martin"|County == "Mower"|County == "Nicollet"|County == "Nobles"|County == "Olmsted"|County == "Rock"|County == "Steele"|County == "Waseca"|County == "Watonwan"|County == "Winona"|County == "Rice" ~ 1,
    County == "Dakota"|County == "Goodhue"|County == "Scott"|County == "Wabasha" ~ 2,
    County == "Hennepin"|County == "Carver" ~ 3,
    County == "Washington" ~ 4,
    County == "Ramsey" ~ 5,
    County == "Benton"|County == "Sherburne"|County == "Wright"|County == "Anoka"|County == "Stearns" ~ 6,
    County == "Becker"|County == "Big Stone"|County == "Chippewa"|County == "Clay"|County == "Clearwater"|County == "Douglas"|County == "Grant"|County == "Kandiyohi"|County == "Kittson"|County == "Lac Qui Parle"|County == "Lake of the Woods"|County == "Lincoln"|County == "Lyon"| County == "Mahnomen"|County == "Marshall"|County == "McLeod"|County == "Meeker"|County == "Murray"|County == "Norman"|County == "Otter Tail"|County == "Pennington"|County == "Pipestone"|County == "Polk"|County == "Pope"|County == "Red Lake"|County == "Redwood"|County == "Renville"|County == "Roseau"|County == "Sibley"|County == "Stevens"|County == "Swift"|County == "Todd"|County == "Traverse"|County == "Wilkin"|County == "Yellow Medicine"|County == "Beltrami"|County == "Cottonwood" ~ 7,
    County == "Aitkin"|County == "Carlton"|County == "Cass"|County == "Chisago"|County == "Cook"|County == "Crow Wing"|County == "Hubbard"|County == "Isanti"|County == "Itasca"|County == "Kanabec"|County == "Koochiching"|County == "Lake"|County == "Mille Lacs"|County == "Morrison"|County == "Pine"|County == "St. Louis"|County == "Wadena" ~ 8))

county_2016$Voters = lapply(county_2016$Voters, function(x) gsub(",", "", x)) %>%
  as.numeric()
```

###Summarizing voter county by district

```{r}
voters_2016 = county_2016 %>%
  group_by(District) %>%
  summarize(Votes = sum(Voters)) %>%
  dplyr::select(Votes)
```

##2012 County Data
```{r}
county_2012 = as.data.frame(extract_tables("data/2012genresults.pdf", page = 1)[[1]], stringsAsFactors = FALSE)
county_2012 = cbind.data.frame(county_2016$County, county_2012, stringsAsFactors = FALSE) %>%
  dplyr::select(-7)
colnames(county_2012) = c("County", "VotersRegAM", "RegElecDay", "Sigs", "RegMilOver", "FedAbsentee", "Voters")
```

##Mutate MUTATE
```{r}
county_2012 = county_2012 %>%
  mutate(District = case_when(
    County == "Blue Earth"|County == "Brown"|County == "Dodge"|County == "Faribault"|County == "Fillmore"|County == "Freeborn"|County == "Houston"|County == "Jackson"|County == "Le Sueur"|County == "Martin"|County == "Mower"|County == "Nicollet"|County == "Nobles"|County == "Olmsted"|County == "Rock"|County == "Steele"|County == "Waseca"|County == "Watonwan"|County == "Winona"|County == "Rice" ~ 1,
    County == "Dakota"|County == "Goodhue"|County == "Scott"|County == "Wabasha" ~ 2,
    County == "Hennepin"|County == "Carver" ~ 3,
    County == "Washington" ~ 4,
    County == "Ramsey" ~ 5,
    County == "Benton"|County == "Sherburne"|County == "Wright"|County == "Anoka"|County == "Stearns" ~ 6,
    County == "Becker"|County == "Big Stone"|County == "Chippewa"|County == "Clay"|County == "Clearwater"|County == "Douglas"|County == "Grant"|County == "Kandiyohi"|County == "Kittson"|County == "Lac Qui Parle"|County == "Lake of the Woods"|County == "Lincoln"|County == "Lyon"| County == "Mahnomen"|County == "Marshall"|County == "McLeod"|County == "Meeker"|County == "Murray"|County == "Norman"|County == "Otter Tail"|County == "Pennington"|County == "Pipestone"|County == "Polk"|County == "Pope"|County == "Red Lake"|County == "Redwood"|County == "Renville"|County == "Roseau"|County == "Sibley"|County == "Stevens"|County == "Swift"|County == "Todd"|County == "Traverse"|County == "Wilkin"|County == "Yellow Medicine"|County == "Beltrami"|County == "Cottonwood" ~ 7,
    County == "Aitkin"|County == "Carlton"|County == "Cass"|County == "Chisago"|County == "Cook"|County == "Crow Wing"|County == "Hubbard"|County == "Isanti"|County == "Itasca"|County == "Kanabec"|County == "Koochiching"|County == "Lake"|County == "Mille Lacs"|County == "Morrison"|County == "Pine"|County == "St. Louis"|County == "Wadena" ~ 8))
```

###To Numeric: 2012 fashion

```{r}
county_2012$Voters = lapply(county_2012$Voters, function(x) gsub(",", "", x)) %>%
  as.numeric()
```

```{r}
voters_2012 = county_2012 %>%
  group_by(District) %>%
  summarize(Votes = sum(Voters)) %>%
  dplyr::select(Votes)
```

###Loading and Cleaning General Results Data for 2016: By Congressional District

```{r, message=FALSE, warning=FALSE}
genResults2016_congDist = read_excel("data/2016genresults.xlsx") %>%
  dplyr::select(CONGDIST, TOTVOTING) %>% 
  group_by(CONGDIST) %>%
  summarise(votes = sum(TOTVOTING)) %>%
  slice(-9)
```

###Loading and Cleaning ACS2016

###NOTE
###NOTE
###NOTE
###NOTE
###NOTE

###demo16 below this line is totally different from the one above it
###the demo16 below is involved in a totally different series of methods

###NOTE
###NOTE
###NOTE
###NOTE
###NOTE

```{r}
demo16 = read_excel("data/ACS_1YR/ACS_16_1YR_S0601.xls")
```

###Appending Results to ACS2016

```{r}
demo16 = as.tibble(bind_cols(demo16, voters_2016)) %>%
  dplyr::select(-1)
```

```{r}
demo16 = lapply(demo16, function(x) gsub(",", "", x))
demo16 = lapply(demo16, function(x) gsub("N", 0, x))
demo16 = as.data.frame(lapply(demo16, function(x) gsub("%", "", x)), stringsAsFactors = FALSE)
demo16 = as.data.frame(lapply(demo16, function(x) as.numeric(x)))
colnames(demo16) = c("population", "under5", "fiveTo17", "eighteenTo24", "tw5To44", "fourty5To55", "fifty5to64", "sixty5To74", "seven5plus", "median_age", "male", "female", "white", "black", "native", "asian", "hawaiianPacific", "other", "mixed", "latinx", "whiteNotLatinx", "neverMarried", "married", "separated", "widowed", "lessThanHSDiploma", "HSGrad", "someCollege", "bachelors", "graduate", "firstincome", "secondincome", "thirdincome","fourth", "fifth", "sixth", "seventh", "eighth", "median_income", "belowPovLine", "secondPovLine", "thirdPoveLine", "votes")
```

```{r}
demo16.train = slice(demo16, 1:7)
demo16.test = slice(demo16, 8) %>%
  dplyr::select(-43)
```

###Demo 2012
```{r}
demo12 = read_csv("data/ACS_1YR/ACS_12_1YR_S0501/ACS_12_1YR_S0501_with_ann.csv", skip = 1) %>%
  dplyr::select(contains("Total; Estimate")) %>%
  dplyr::select(-contains("12 MONTHS")) %>%
  dplyr::select(-contains("ROOMS")) %>%
  dplyr::select(-contains("CLASS")) %>%
  dplyr::select(-contains("With related")) %>%
  dplyr::select(-contains("One race")) %>%
  dplyr::select(-contains("SCHOOL")) %>%
  slice(-1)

industry_demo12 = demo12 %>%
  dplyr::select(contains("INDUSTRY"))

voters_12_for_demo = voters_2012[3:5, ]
demo12 = bind_cols(demo12, voters_12_for_demo)
industry_demo12 = bind_cols(industry_demo12, voters_12_for_demo)
```

####Modelling

```{r}
regfit.full=regsubsets(Votes~., data = industry_demo12)
industry2012_fit = lm(industry_demo12$Votes~industry_demo12$`Total; Estimate; INDUSTRY - Finance and insurance, and real estate and rental and leasing`, data = industry_demo12)
summary(industry2012_fit)
plot(industry_demo12$`Total; Estimate; INDUSTRY - Finance and insurance, and real estate and rental and leasing`, industry_demo12$Votes)
```

####Checking Fit Summary

```{r}
regfit.full=regsubsets(votes~., data = demo16.train)
summary(regfit.full)
```

####More Fit Summary

```{r}
demo16.fit = lm(votes ~ mixed + thirdincome + eighth + thirdPoveLine, data = demo16.train)
predict(demo16.fit, demo16.test)
summary(demo16.fit)
```

###Formatting Data15

```{r} 
colnames(demo15) = demo15[1,]
demo15 = as.tibble(slice(demo15[-1,]))
demo15 = dplyr::select(demo15, 2:9)
```

#### Let's try to clean up this data a little bit

```{r}
elections1 <- elections %>%
  filter(Year <= 2016) 

#This ain't right
elect_rm_na <- elections1 %>%
  filter(Prcnt_Turnout == "No Data")
  

#dist %>%
  #gather(key = var_name, value = value, 2:ncol(dist)) %>%
  #spread_(key = names(dist)[1], value = 'value')

#dist.df <- as.data.frame(dists)

#t_df <- data.table::transpose(dist.df)
#colnames(t_df) <- rownames(dist.df)
#rownames(t_df) <- colnames(dist.df)

#dists_t <- as_tibble(t_df)
#write_csv(dists_t, "dists_t.csv")




```

#### Basic Visualization

```{r}
#ggplot(data = elections) +
#  geom_point(mapping = aes(x = Year, y = Prcnt_Turnout))

elections1 %>%
  gf_point(Prcnt_Turnout ~ Year) %>%
    gf_lm(Prcnt_Turnout ~ Year, color = "blue")

elections1 %>%
  gf_point(Num_Voters ~ Year) %>%
  gf_point(Est_Num_Elg_Voters ~ Year) %>%
  gf_lm(Est_Num_Elg_Voters ~ Year)
```

##Attempt At Forecasting

```{r}
district_registration = 
  read_excel("data/minnesota-voter-registration-by-county-since-2000.xlsx") %>%
  t() %>%
  as.tibble()

colnames(district_registration) = district_registration[1,]
district_registration = slice(district_registration, -1)
```

```{r}
plot.ts(district_registration$Faribault)
```

```{r}
fts = ts(district_registration$Faribault, frequency=3)
decomp = stl(fts, s.window="periodic")
deseasonal_cnt <- seasadj(decomp)
```

```{r}
fit = auto.arima(deseasonal_cnt, seasonal=FALSE)
fcast <- forecast(fit, h=30)
plot(fcast)

```

```{r}
ge2008 = read_excel("data/elections/2008NovemberGeneralElection.xlsx", skip = 1) %>%
  filter(X__1 == "Minnesota") %>%
  mutate(GeneralElection = "yes", year = 2008)

pe2008 = read_excel("data/elections/2008PrimaryElections.xlsx", skip = 1) %>%
  filter(`State/Territory` == "Minnesota") %>%
  mutate(GeneralElection = "no", year = 2008) %>%
  select(-Date, -3, -9)

ge2010 = read_excel("data/elections/2010NovemberGeneralElection.xlsx", skip = 1) %>%
  filter(X__1 == "Minnesota") %>%
  mutate(GeneralElection = "yes", year = 2010)

ge2012 = read_excel("data/elections/2012NovemberGeneralElection.xlsx", skip = 1) %>%
  filter(X__1 == "Minnesota") %>%
  mutate(GeneralElection = "yes", year = 2012)

pe2012 = read_excel("data/elections/2012PrimaryElections.xlsx", skip = 1) %>%
  filter(`State/Territory` == "Minnesota") %>%
  mutate(GeneralElection = "no", year = 2012) %>%
  select(-Date)

pe2012[1, 6] = 17376
pe2012[1, 9] = 66292

pe2012 = pe2012 %>% slice(1) %>%
  select(-2, -8)
  

ge2014 = read_excel("data/elections/2014NovemberGeneralElection.xlsx", skip = 1) %>%
  filter(X__1 == "Minnesota") %>%
  mutate(GeneralElection = "yes", year = 2014) %>%
  select(-15)

ge2016 = read_excel("data/elections/2016NovemberGeneralElection.xlsx", skip = 1) %>%
  filter(X__1 == "Minnesota") %>%
  mutate(GeneralElection = "yes", year = 2016) %>%
  select(-2, -3, -17)

pe2016 = read_excel("data/elections/2016PrimaryElections.xlsx", skip = 1) %>%
  filter(`State` == "Minnesota") %>%
  mutate(GeneralElection = "no", year = 2016) %>%
  select(-1, -3, -4, -10, -12, -13)

primary = bind_rows(pe2008, pe2012, pe2016)
general = bind_rows(ge2008, ge2010, ge2012, ge2014, ge2016)
```

```{r}
yes = lm(ruff_turnout~Under5 + FiveTo17 + FortyFiveTo54 + White + Hispanic + White_alone + Now_married_not_separated + Some_college_or_associate_degree + One_9999_loss, data = trainingData)

mean((testingData$ruff_turnout - predict.lm(yes, testingData)) ^ 2)

```