---
title: "MinneMudac 2018"
author: "Elliot Pickens & Chiraag Gohel"
date: "11/3/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, echo = FALSE, warning=FALSE, message=FALSE}

library(aod)
library(boot)
library(broom)
library(car)
library(caret)
library(caretEnsemble)
library(dplyr)
library(forecast) 
library(GGally)
library(ggformula)
library(ggplot2)
library(ggthemes)
library(glmnet)
library(gridExtra)
library(lattice)
library(leaps)
library(MASS)
library(RANN)
library(readr)
library(readxl)
library(skimr)
library(stringr)
library(tabulizer)
library(tibble)
library(tidyr)
library(tidyselect)
library(tidyverse)
library(tseries)
```


## Statewide Turnout from 2008-2016

```{r}
gen_turnout <- read_xlsx("data/turnout_2000-2016.xlsx")

gen_turnout %>%
  gf_point(Percent.Turnout ~ Year, ylab = "Percent Turnout", title = "Statewide General Election Turnout") %>%
  gf_lm()
```

## Turnout by District from 2008-2016

```{r}
graph_data <- read_xlsx("data/test_data.xlsx")



cg1 <- graph_data %>%
  filter(Subject == "CG1")
cg2 <- graph_data %>%
  filter(Subject == "CG2")
cg3 <- graph_data %>%
  filter(Subject == "CG3")
cg4 <- graph_data %>%
  filter(Subject == "CG4")
cg5 <- graph_data %>%
  filter(Subject == "CG5")
cg6 <- graph_data %>%
  filter(Subject == "CG6")
cg7 <- graph_data %>%
  filter(Subject == "CG7")
cg8 <- graph_data %>%
  filter(Subject == "CG8")



#Using rough turnout


a = cg1 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG1", ylab = "Estimate of Turnout Percentage")
b = cg2 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG2", ylab = "Estimate of Turnout Percentage")
d = cg3 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG3", ylab = "Estimate of Turnout Percentage")
c = cg4 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG4", ylab = "Estimate of Turnout Percentage")
e = cg5 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG5", ylab = "Estimate of Turnout Percentage")
f = cg6 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG6", ylab = "Estimate of Turnout Percentage")
g = cg7 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG7", ylab = "Estimate of Turnout Percentage")
h = cg8 %>%
  gf_point(ruff_turnout ~ Year, title = "Turnout Estimate CG8", ylab = "Estimate of Turnout Percentage")

a1 = ggplot() + 
  geom_point(aes(x = Year, y = ruff_turnout), data = cg1) +
  labs(title = "Turnout Estimate: Cong. District 1", y = "Estimate of Turnout Percentage")

a2 = ggplot() + 
  geom_point(aes(x = Year, y = ruff_turnout), data = cg2) +
  labs(title = "Turnout Estimate: Cong. District 2", y = "")
  
a3 = ggplot() + 
  geom_point(aes(x = Year, y = ruff_turnout), data = cg3) +
  labs(title = "Turnout Estimate: Cong. District 3", y = "Estimate of Turnout Percentage")

a4 = ggplot() + 
  geom_point(aes(x = Year, y = ruff_turnout), data = cg4) +
  labs(title = "Turnout Estimate: Cong. District 4", y = "")

a5 = ggplot() + 
  geom_point(aes(x = Year, y = ruff_turnout), data = cg5) +
  labs(title = "Turnout Estimate: Cong. District 5", y = "Estimate of Turnout Percentage")

a6 = 
  ggplot() + 
  geom_point(aes(x = Year, y = ruff_turnout), data = cg6) +
  labs(title = "Turnout Estimate: Cong. District 6", y = "")

a7 = ggplot() + 
  geom_point(aes(x = Year, y = ruff_turnout), data = cg7) +
  labs(title = "Turnout Estimate: Cong. District 7", y = "Estimate of Turnout Percentage")

a8 = ggplot() + 
  geom_point(aes(x = Year, y = ruff_turnout), data = cg8) +
  labs(title = "Turnout Estimate: Cong. District 8", y = "")

grid.arrange(a1, a2, a3, a4)

```

##Turnout by District from 2008-2016
```{r}
grid.arrange(a5, a6, a7, a8)
```

##Datums
```{r, message=FALSE, warning=FALSE, echo=FALSE}

elec16 <- read_xlsx("data/dist_elec_stats/2016-general-federal-state-results-by-precinct-official-1.xlsx")
elec14 <- read_xlsx("data/dist_elec_stats/2014-general-federal-state-results-by-precinct-official.xlsx")
elec12 <- read_xlsx("data/dist_elec_stats/2012mngeneralelectionresults_official_postrecounts.xlsx")
elec10 <- read_xls("data/dist_elec_stats/2010_general_results_final.xls")
elec08 <- read_xls("data/dist_elec_stats/2008_general_results.xls")

vote16 <- elec16 %>%
  group_by(CONGDIST) %>%
  summarise(tot_votes = sum(TOTVOTING))

vote16 <- vote16 %>%
  dplyr::select(tot_votes) %>%
  filter(tot_votes < 1000000)

vote14 <- elec14 %>%
  group_by(CONGDIST) %>%
  summarise(tot_votes = sum(TOTVOTING)) %>%
  dplyr::select(tot_votes)

vote12 <- elec12 %>%
  group_by(CONGDIST) %>%
  summarise(tot_votes = sum(TOTVOTING))

vote12 <- vote12 %>%
  dplyr::select(tot_votes) %>%
  filter(tot_votes < 1000000)

vote10 <- elec10 %>%
  group_by(CG) %>%
  summarise(tot_votes = sum(TotVoters))

vote10 <- vote10 %>%
  dplyr::select(tot_votes) %>%
  filter(tot_votes < 1000000)

vote08 <- elec08 %>%
  group_by(CG) %>%
  summarise(tot_votes = sum(TotVoters))

vote08 <- vote08 %>%
  dplyr::select(tot_votes) %>%
  filter(tot_votes < 1000000)

demo16 <- read_xls("data/ACS_1YR/ACS_16_1YR_BasicER.xls")
demo14 <- read_xls("data/ACS_5YR/Basic/ACS_14_5YR_Ber.xls")
demo12 <- read_xls("data/ACS_5YR/Basic/ACS_12_5YR_Ber.xls")
demo10 <- read_xls("data/ACS_5YR/Basic/ACS_10_5YR_Ber.xls")
demo08 <- read_xls("data/ACS_1YR/ACS_08_1YR_BasicER.xls")

temp16 <- demo16 %>%
  mutate(tot_votes = vote16$tot_votes)

temp14 <- demo14 %>%
  mutate(tot_votes = vote14$tot_votes)

temp12 <- demo12 %>%
  mutate(tot_votes = vote12$tot_votes)

temp10 <- demo10 %>%
  mutate(tot_votes = vote10$tot_votes)

temp08 <- demo08 %>%
  mutate(tot_votes = vote08$tot_votes)

temp <- bind_rows(temp16, temp14, temp12, temp10, temp08)

temp <- temp %>% rename(Tot_Pop = `Total population`) 
  
temp$Tot_Pop <- as.numeric(gsub(",","",temp$Tot_Pop))

vars <- names(temp)[3:38]
temp <- temp %>% mutate_each(funs(as.numeric(gsub("%", "", ., fixed = TRUE))/100), vars)

temp <- temp %>%
  mutate(over18 = EighteenTo24 + TwentyfiveTo44 + FortyFiveTo54 + FiftyfiveTo64 + SixtyfiveTo74 + Seventyfive_plus)

temp1 <- temp %>% 
  mutate(ruff_turnout = tot_votes / (Tot_Pop * over18)) 

gen_elec_08_16 <- temp1 %>%
  dplyr::select(-Tot_Pop, -tot_votes)

sum(is.na(gen_elec_08_16))

#remove the sole na 

#I am choosing to replace the sole missing value that is already close to 0
#with the 2014 value from the same district
#assuming the the percentage of native people has not changed greatly
#the new value is 0.003 (basically NN -- nearest neighbor method)

gen_elec_08_16 <- gen_elec_08_16 %>%
  replace_na(list(American_Indian_and_Alaska_Native = 0.003))

#remove names

gen_elec_no_names <- gen_elec_08_16 %>%
  dplyr::select(-Subject)

demo17_b <- read_xls("data/ACS_1YR/ACS_17_1YR_BasicER.xls")

demo17_b <- demo17_b %>% rename(Tot_Pop = `Total population`) 
  
demo17_b$Tot_Pop <- as.numeric(gsub(",","",demo17_b$Tot_Pop))

vars <- names(demo17_b)[3:38]
demo17_b <- demo17_b %>% mutate_each(funs(as.numeric(gsub("%", "", ., fixed = TRUE))/100), vars)

demo17_b <- demo17_b %>%
  mutate(over18 = EighteenTo24 + TwentyfiveTo44 + FortyFiveTo54 + FiftyfiveTo64 + SixtyfiveTo74 + Seventyfive_plus)

test17 <- demo17_b %>%
  dplyr::select(-Tot_Pop)

#remove names

test17 <- test17 %>%
  dplyr::select(-Subject)

#fill in NA values

####Will go back and re-Preprocess everything correctly in a minute

####For now I'm going to be lazy
####ANNNDDDDD.....

test17 <- test17 %>%
  replace_na(list(American_Indian_and_Alaska_Native = 0.000))

set.seed(100)

trainRowNums <- createDataPartition(gen_elec_no_names$over18, p = 0.8, list = FALSE)

trainingData <- gen_elec_no_names[trainRowNums,]

testingData <- gen_elec_no_names[-trainRowNums,]

#Store extra data for later use
x = trainingData[, 1:37]
y = trainingData$ruff_turnout


```

```{r, echo=FALSE}
skimmed <- skim_to_wide(gen_elec_no_names)
skimmed$hist
```


## Intro

## Data Carpentry

- Demographic data sourced from the ACS (American Community Survey).

- Election results sourced from the Office of the Minnesota Secretary of State.

## Regsubsets: Visualization

```{r, warning=FALSE, message=FALSE}
bestFit = (regsubsets(ruff_turnout~., data = trainingData))
bestFitSummary = summary(bestFit)
data_frame(Cp = bestFitSummary$cp,
           BIC = bestFitSummary$bic,
           AdjR2 = bestFitSummary$adjr2) %>%
    mutate(id = row_number()) %>%
    gather(value_type, value, -id) %>%
    ggplot(aes(id, value, col = value_type)) +
    geom_line() + geom_point() + ylab('') + xlab('Number of Variables Used') +
    facet_wrap(~ value_type, scales = 'free') + 
    scale_x_continuous(breaks = 1:10) +
    ggtitle("Error Rates and Fit Values for Various Regressions")
```

##Regsubsets: Explained

* $C_p$ and BIC rates are various error terms used to analyze subset model selection
* Looking to maximize the adjusted R-squared value, and minimize the other two error rates
* Optimal variable selection: 3-5 variables

##Regsubsets: BIC Plot

```{r}
plot(bestFit, ylab = "BIC Values", main = "BIC Optimizaion")
```

##Regsubsets: Predictor Selection
```{r}
fourPredictors = as.tibble(bestFitSummary$outmat[4, ]) %>%
  as.data.frame()

fourPredictors
```

##Regression Analysis

```{r, echo=TRUE}
newFit = glm(ruff_turnout~Under5 + FiveTo17 + 
             FortyFiveTo54 + One_9999_loss,
             data = trainingData)
```

- Our model can be depicted as: 

$$Y = -0.92 + 10.13X_1 - 3.39X_2 + 9.32X_3 + 2.28X_4$$

Where:

- <font size = "4">$Y$ = Voter turnout</font>
- <font size = "4">$X_1$ = Percentage of district population under the age of five</font>
- <font size = "4">$X_2$ = Percentage of district population within the ages of five to seventeen</font>
- <font size = "4">$X_3$ = Percentage of district population within the ages of forty-five to fifty-four</font>
- <font size = "4">$X_4$ = Percentage of distrcit population with an annual income of $20,000</font>

```{r}
delta = cv.glm(trainingData, newFit)$delta[1]
mseReg = mean((testingData$ruff_turnout - predict.lm(newFit, testingData)) ^ 2)
```

#BIC
newFit.step <- stepAIC(newFit, scope = list(lower = ~ 1, upper = ~ .), direction = "both", k = log(nrow(trainingData)))

#AIC
newFit.step <- stepAIC(newFit, scope = list(lower = ~ 1, upper = ~ .), direction = "both", k = log(nrow(trainingData)))

#Nothing Happens when it is run on the model you put in!!! So we should be good

mean((testingData$ruff_turnout - predict.lm(newFit, testingData)) ^ 2)
#You might want to change the labels on this
plot(newFit$residuals)
```

##Black Boxes

```{r}
set.seed(100)

# Train the model using MARS
model_svmRadial = train(ruff_turnout ~ ., data=trainingData, method='svmRadial', tuneLength=15)

model_xgbDART = train(ruff_turnout ~ ., data=trainingData, method='xgbDART', tuneLength=5, verbose=F)

model_rf = train(ruff_turnout ~ ., data=trainingData, method='rf')

model_mars = train(ruff_turnout ~ ., data=trainingData, method='earth')

models_compare <- resamples(list(RF=model_rf, MARS=model_mars, SVM=model_svmRadial, xgbDART=model_xgbDART))

scales <- list(x=list(relation="free"), y=list(relation="free"))
bwplot(models_compare, scales=scales)
```


##Ensembles 

```{r}
set.seed(100)
algos <- c('rf', 'earth', 'svmRadial')

ensemble <- caretEnsemble::caretList(ruff_turnout ~ ., data=trainingData, methodList=algos) 
results <- resamples(ensemble)

#MSE
mean((testingData$ruff_turnout - stack_pred) ^ 2)

resid <- (testingData$ruff_turnout - stack_pred)
resid <- data.frame(resid, seq(1:7))
resid %>%
  gf_point(resid ~ seq.1.7.) %>%
  gf_hline(yintercept = 0)

scales <- list(x=list(relation="free"), y=list(relation="free"))
bwplot(results, scales=scales)
```


##Quantile Regression Neural Network

```{r}
model_QRNN = train(ruff_turnout ~ ., data=trainingData, method='qrnn')
plot(model_QRNN)
```


